---
title: "assign4"
output: html_notebook
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

```{r}
library(lubridate)
library(stringr)
library(RVerbalExpressions)
```


# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 
```{r}
ymd("2015-01-01") + months(0:11)
```

Write a function that given your birthday (as a date), returns how old you are in years.
```{r}
age <- function(birthday) {
  (birthday %--% today()) %/% years(1)
}
age(ymd("1997-01-29"))
```

Write a function that given your birthday, returns the day of the week you were born on. 
```{r}
weekday <- function(birthday) {
  wday(birthday, label = TRUE)
}
weekday(ymd("1997-01-29"))
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)
```{r}
# Regular expressions
str_view(stringr::words, ".......", match = TRUE)
```

```{r}
# Verbal expressions
wordsrx <- rx() %>% 
  rx_something() %>% 
  rx_repeat_previous(7) %>% 
  grepl(stringr::words)
stringr::words[wordsrx == TRUE]
```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)
```{r}
# Regular expressions
str_subset(stringr::words, "^[^aeiou]+$")
```

```{r}
# Verbal expressions
consonantsrx <- rx() %>% 
  rx_any_of("aeiou") %>% 
  grepl(stringr::words) 
stringr::words[consonantsrx == FALSE]
```


Empirically verify the rule “i before e except after c”.
```{r}
# Regular expressions
str_subset(stringr::words, "(cei|[^c]ie)")
```
```{r}
# Regular expressions
str_subset(stringr::words, "(cie|[^c]ei)")
```

```{r}
# Verbal expressions
rulerx <- rx() %>% 
  rx_something_but("cei") %>%
  rx_either_of("cie", "ei") %>%
  grepl(stringr::words)
stringr::words[rulerx == TRUE]
```


```{r}
# Verbal expressions
rulerx <- rx() %>% 
  rx_something_but(value = "cie") %>%
  rx_either_of("cei", "ie") %>%
  grepl(stringr::words)
stringr::words[rulerx == TRUE]

rulerx <- rx() %>% 
  rx_find("cei") %>% 
  grepl(stringr::words)
stringr::words[rulerx == TRUE]
```

Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.
```{r}
x <- c("615-123-4567", "615.123.4567","615-1234-567")
```

```{r}
# Regular expressions
str_view(x, "\\d{3}?[ -\\.]\\d{3}?[ -\\.]\\d{4}")
```

```{r}
# Verbal expressions
telrx <- rx() %>% 
  rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>%
  grepl(x) %>% 
  print()
x[telrx]
```



# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

3. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

